The \dealii{} Library, Version 8.5

### 2017-03-20 8.5/paper.tex
Minor edits.

\texttt{CellDataStorage} can work with arbitrary kinds of data defined
to live on a cell as long as the corresponding data type implements a
certain interface. As an example,
the abstract \texttt{TransferableQuadraturePointData} class provides
a generic interface to facilitate several low-level operations
that were previously tedious or technically challenging to implement.
For instance, when user's custom data type is derived from \texttt{TransferableQuadraturePointData}
and stored at quadrature points using \texttt{CellDataStorage},
the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
can transfer this data (assuming that it is continuous within a cell)
when performing $h$-adaptive refinement of
\texttt{parallel::distributed::Triangulation}. Not only does it perform an
$L^2$-projection of the specified user data between quadrature
points, but it also ships the data automatically between MPI processes.

>>>>

\texttt{CellDataStorage} can work with arbitrary kinds of data defined
to live on a cell as long as the corresponding data type implements a
certain interface. As an example,
the abstract class \texttt{TransferableQuadraturePointData} provides
a generic interface to facilitate several low-level operations
that were previously tedious or technically challenging to implement.
For instance, when a user's custom data type is derived from \texttt{TransferableQuadraturePointData}
-- a data type that stores information at the quadrature points of cells using
\texttt{CellDataStorage} --,
then the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer} class
can transfer this data during
$h$-adaptive refinement from parent to children and the other way around
(interpreting the data on quadrature points as discrete representations of an
underlying continuous field),
as well as from one processor to another during repartitioning.
